PNSAC Merchandise

### 2013-10-17 pnsac/newsletter/article_Special.tex
Newsletter: final changes incorporated.

Have a look at our Facebook page,
{\normalfont\color{blue}\texttt{\href{https://www.facebook.com/media/set/?set=a.610706705637878.1073741851.284829008225651&type=1}{PNSAC
      Merchandise}}}, to see what we're offering, and place your
orders by sending an email message to the following address
\email{pnsac.merchandise@gmail.com}.

For members in the Ottawa-Gatineau region, you can arrange to pick up
your merchandise at the Canada Aviation and Space museum any Monday or
Tuesday, between 10:00 AM and 3:00 PM. We can also ship your purchases
to you for an extra fee. Please specify museum pickup or shipping with
your order.

Merchandise is also available during our Quarterly Meetings
at CAVM.

>>>>

See our Facebook page,
{\normalfont\color{blue}\texttt{\href{https://www.facebook.com/media/set/?set=a.610706705637878.1073741851.284829008225651&type=1}{PNSAC
      Merchandise}}}, for details about what we're offering, and place your
orders by sending an email message to the following address
\email{pnsac.merchandise@gmail.com}.

For members in the Ottawa-Gatineau region, you can arrange to pick up
your merchandise at the Canada Aviation and Space Museum any Monday or
Tuesday, between 10:00 AM and 3:00 PM. We can also ship your purchases
to you for an extra fee. Please specify museum pickup or shipping with
your order.

Merchandise is also available during our Quarterly Meetings
at CASM.
